Do More Subdivisions in Wards Increase Turnout? An Analysis of the 2022 Toronto Municipal Election

### 2023-06-01 outputs/paper/paper.qmd
Added additional section headers and wrote a further explanation about the voter statistics data set

@@

>>>>

For the purpose of this paper, I did not include the Advance Vote and Mail In Voting subdivisions when counting the total number of subdivisions per ward. Firstly, there are only two Advance Vote locations distributed across every ward, meaning residents have to be motivated to travel farther away from their home to cast their ballot. Secondly, Mail In Voting requires applying online through Toronto Elections and then returning the completed Mail In Voting package by dropping it in a Canada Post mailbox or hand delivering it to one of the Toronto Elections drop boxes at select locations. Voters need to be more organized and motivated to vote in advance of election day.

@@

```
### Discussion

### Conclusion

### References
